---
title: "Phase 1 DSAAdvancedR Package"
author: "Nicholas Jacob"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DSAAdvancedR)
```

## Test Run

I have loaded my package in the r setup block of code with `library(DSAAdvancedR)`.  We will error test it here.  First we load the data.  This data is as prescribed in the submission details and repeats what is used in the example.

```{r example}
 set.seed(21);x <-rnorm(30,5,2);
 set.seed(23); y<- rnorm(40, 3,2);
 alpha <- 0.05
 obj <- myttest(x = x, y = y, alpha = 0.05)
 class(obj)
 print(obj)
```

We see the printing of the class, then the dataframe, alpha, confidence interval and p value.  

## Error Testing

I never really trust these packages and often like to make computations from first principals.  I will do that here.  For two variable $t$ test with equal variance, the standard error, $SE$, is
$$
SE = s_p\sqrt{\frac1{n_1} +\frac1{n_2}}.
$$
Where $s_p$ is the pooled standard deviation,
$$
s_p = \sqrt{\frac{(n_1-1)s_x^2 + (n_2-1)s_y^2}{n_1+n_2-2}}
$$

We compute that here with the data above
```{r se}
sx <- sd(x)
sy <- sd(y)
nx <- length(x)
ny <- length(y)
sp <- sqrt(((nx-1)*sx^2 + (ny-1)*sy^2)/(nx+ny-2))
sp
```

Then the $t$ value is

$$
t = \frac{\overline{x} - \overline{y}}{SE}
$$

Doing this in R
```{r tcomp}
xbar <- mean(x)
ybar <- mean(y)
se <- sp*sqrt(1/nx + 1/ny)
t<- (xbar - ybar)/(se)
t
```

Converting that into a $p$ value:

```{r pval}
2*pt(-1*t,nx+ny-2)
```

For the confidence interval, we use the formula
$$
(\overline x - \overline y) \pm t^*SE
$$
I need to compute the $t^*$
```{r tstar}
tstar = qt(0.975, nx+ny-2)
tstar
```
Then we compute the CI
```{r CI}
ci = c(xbar - ybar -tstar*se,xbar - ybar +tstar*se)
ci
```
Everything tests out!  I have never found a test in R I didn't agree with just always like to check how it is working for a stats point of view.
